Supplementary Information: Tropical tree drought sensitivity is jointly shaped by drought characteristics, species adaptations, and individual microenvironments

### 2025-06-26 doc/manuscript_hkk_drought_sensitivity.Rmd
results

Median annual increment varied among species with *`r tree.time.sp$spfull[1]`* the lowest (`r tree.time.sp$inc_annual_med[1]` $\pm$ `r tree.time.sp$inc_annual_sd[1]` mm) and *`r tree.time.sp$spfull[nrow(tree.time.sp)]`* the highest (`r tree.time.sp$inc_annual_med[nrow(tree.time.sp)]` $\pm$ `r tree.time.sp$inc_annual_sd[nrow(tree.time.sp)]` mm) among the `r nrow(tree.time.sp)` species analysed.  
Median species responses to the 2010 and 2020 droughts were variable, but all species had lower median increments than a typical year in 2015. 
In 2010, species-level sensitivities ranged from `r sens.sp[sens.sp$yr==2010,]$sens_med[1]` for *`r sens.sp[sens.sp$yr==2010,]$spfull[1]`* to `r sens.sp[sens.sp$yr==2010,]$sens_med[nrow(sens.sp)/3]` for *`r sens.sp[sens.sp$yr==2010,]$spfull[nrow(sens.sp)/3]`*. 
In 2015, these ranged from `r sens.sp[sens.sp$yr==2015,]$sens_med[1]` for *`r sens.sp[sens.sp$yr==2015,]$spfull[1]`* to `r sens.sp[sens.sp$yr==2015,]$sens_med[nrow(sens.sp)/3]` for *`r sens.sp[sens.sp$yr==2015,]$spfull[nrow(sens.sp)/3]`* and in 2020 from `r sens.sp[sens.sp$yr==2020,]$sens_med[1]` for *`r sens.sp[sens.sp$yr==2020,]$spfull[1]`* to `r sens.sp[sens.sp$yr==2020,]$sens_med[nrow(sens.sp)/3]` for *`r sens.sp[sens.sp$yr==2020,]$spfull[nrow(sens.sp)/3]`*.

>>>>

Median annual increment varied among species, with *`r tree.time.sp$spfull[1]`* the lowest (`r tree.time.sp$inc_annual_med[1]` $\pm$ `r tree.time.sp$inc_annual_sd[1]` mm) and *`r tree.time.sp$spfull[nrow(tree.time.sp)]`* the highest (`r tree.time.sp$inc_annual_med[nrow(tree.time.sp)]` $\pm$ `r tree.time.sp$inc_annual_sd[nrow(tree.time.sp)]` mm) among the `r nrow(tree.time.sp)` species analysed.
Median species responses to the 2010 and 2020 droughts were variable, but no species had higher median increments than a typical year in 2015. <!--KAT reworded here because Mitrephora thorelii was very slightly positive-->
In 2010, species-level sensitivities ranged from `r sens.sp[sens.sp$yr==2010,]$sens_med[1]` for *`r sens.sp[sens.sp$yr==2010,]$spfull[1]`* to `r sens.sp[sens.sp$yr==2010,]$sens_med[nrow(sens.sp)/3]` for *`r sens.sp[sens.sp$yr==2010,]$spfull[nrow(sens.sp)/3]`*. 
In 2015, these ranged from `r sens.sp[sens.sp$yr==2015,]$sens_med[1]` for *`r sens.sp[sens.sp$yr==2015,]$spfull[1]`* to `r sens.sp[sens.sp$yr==2015,]$sens_med[nrow(sens.sp)/3]` for *`r sens.sp[sens.sp$yr==2015,]$spfull[nrow(sens.sp)/3]`*, and in 2020 from `r sens.sp[sens.sp$yr==2020,]$sens_med[1]` for *`r sens.sp[sens.sp$yr==2020,]$spfull[1]`* to `r sens.sp[sens.sp$yr==2020,]$sens_med[nrow(sens.sp)/3]` for *`r sens.sp[sens.sp$yr==2020,]$spfull[nrow(sens.sp)/3]`*.
